plackett_luce_monster

### 2022-07-07 inst/plackett_luce_monster.Rmd
slight change to observation

```{r,defineredbuslf}
`RB_BB_LF` <- function(s){
    ec <- c(C=1,T=2,RB=3,BB=3,W=4) # equivalence classes
    h <- c(1,1,s,1)                # strength of support
    (
        cheering3(v=c("RB","BB","C" ,"T","W"),e=ec,h=h)*7 + 
        cheering3(v=c("BB","RB","T" ,"C","W"),e=ec,h=h)*4 + 
        cheering3(v=c("T" ,"BB","RB","C","W"),e=ec,h=h)*5 + 
        cheering3(v=c("W" ,"BB","RB","T","C"),e=ec,h=h)*8 + 
        cheering3(v=c("C" ,"RB","BB","W","T"),e=ec,h=h)*9 + 
        cheering3(v=c("BB","C" ,"RB","T","W"),e=ec,h=h)*5
    )
}
```

Above, we see from the function body that he reported `RB,BB,C,T,W`
seven times, `BB,RB,T,C,W` four times, and so on; perhaps his ranking
depends on the weather or how tired he is on any given day.  Observe
that in almost every case he ranks `RB` and `BB` consecutively.
Function `RB_BB_LF()` takes argument `s` that quantifies the perceived
similarity between `RB` and `BB`.  For example:

@@

```{r,label=proflikeredbus,cache=TRUE}
o <- function(s){maxp(RB_BB_LF(s),give=TRUE,n=1)$likes} # optimand
s <- exp(seq(from=log(1.3),to=log(37),len=17)) # putative similarity measures
L <- sapply(s,o)
L <- L-max(L)
```

@@

```{r,label=LRT_RB,cache=TRUE}
(suppdif <- o(osup$maximum) - o(1))
```

Falling just shy of Edwards's two-units-of-support criterion.

>>>>

```{r,defineredbuslf}
`RB_BB_LF` <- function(s){
    ec <- c(C=1,T=2,RB=3,BB=3,W=4) # equivalence classes
    h <- c(1,1,s,1)                # strength of support
    (
        cheering3(v=c("RB","BB","C" ,"T","W"),e=ec,h=h)*3 + 
        cheering3(v=c("BB","RB","T" ,"C","W"),e=ec,h=h)*2 + 
        cheering3(v=c("T" ,"BB","RB","C","W"),e=ec,h=h)*2 + 
        cheering3(v=c("W" ,"BB","RB","T","C"),e=ec,h=h)*4 + 
        cheering3(v=c("C" ,"RB","BB","W","T"),e=ec,h=h)*4 + 
        cheering3(v=c("BB","C" ,"RB","T","W"),e=ec,h=h)*3
    )
}
```

Above, we see from the function body that he reported `RB,BB,C,T,W`
three times[first row], `BB,RB,T,C,W` twice [second row], and so on;
perhaps his ranking depends on the weather or how tired he is on any
given day.  Observe that in almost every case he ranks `RB` and `BB`
consecutively.  Function `RB_BB_LF()` takes argument `s` that
quantifies the perceived similarity between `RB` and `BB`.  For
example:

@@

```{r,label=proflikeredbus,cache=TRUE}
o <- function(s){maxp(RB_BB_LF(s),give=TRUE,n=1)$likes} # optimand
s <- exp(seq(from=log(1.3),to=log(47),len=17)) # putative similarity measures
L <- sapply(s,o)
L <- L-max(L)
```

@@

```{r,label=LRT_RB,cache=TRUE}
(suppdiff <- o(osup$maximum) - o(1))
```

Easily satisfying Edwards's two-units-of-support criterion; Wilks gives us an asymptotic $p$-value:

```{r,label=RBBBpval}
pchisq(suppdiff*2,df=1,lower.tail=FALSE)
```
